A general Nullstellensatz for generalised spaces

### 2019-04-11 slides-birmingham2019.tex
Picture of the black hole in M87

@@

  \textbf{Remark.} Externalizing the internal classifying
  topos~$\Set[\TT][\ul{\TT}/U_\TT]$ yields the classifying topos
  of~$\TT$-homomorphisms.
\end{frame}

>>>>

{\usebackgroundtemplate{\begin{minipage}{\paperwidth}\hspace*{-1.7cm}\includegraphics[height=\paperheight]{black-hole-m87}\end{minipage}}
\begin{frame}[plain]
  \vspace*{\paperheight}\vspace*{-1cm}\scriptsize
  \centering
  \textcolor{white}{Fig.: The Event Horizon Telescope picture of the central black
  hole in the galaxy M87}
  \par
\end{frame}}
\addtocounter{framenumber}{-1}

@@

  \textbf{Remark.} Externalising the internal classifying
  topos~$\Set[\TT][\ul{\TT}/U_\TT]$ yields the classifying topos
  of~$\TT$-homomorphisms.
\end{frame}
